### 2015-04-21 paper.tex
Write about performance figures

Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh.
Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur
fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt
sit amet feugiat eget, ullamcorper sed velit. Sed non aliquet felis. Lorem ipsum
dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium
imperdiet. Sed suscipit iaculis mi at feugiat.

@@

>>>>

Mean rotor power and drag coefficients for multiple Reynolds numbers are plotted
versus tip speed ratio in Fig.~\ref{fig:cp-curves} and Fig.~\ref{fig:cd-curves},
respectively. $C_P$ is shown to increase in general with $Re$, along with a
reduction in the optimal tip speed ratio, due to stall delay. These effect
diminish with increasing $Re$, which is expected as the blade boundary layers
transition from laminar to turbulent \cite{Lissaman1983,
Bachant2015-RVAT-Re-dep}. The rotor drag coefficient curves show similar
effects, but vary much less dramatically from each other.

@@

The behavior of the power coefficient at $\lambda=3.1$ is plotted in
Fig.~\ref{fig:cp-re-dep}, where once again the increase in $C_P$ with $Re$ is
highlighted. We see that the power coefficient of the turbine increases
dramatically below $Re_D = 1 \times 10^6$ or $Re_c \approx 2 \times 10^5$,
beyond which there appears to be a small, linear, positive trend. The tendency
of $C_P$ to continue increasing slightly could be an effect of lower virtual
camber when compared to the strong $Re$-indepdendence of the higher $c/R$
UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.
